---
title: "Boot_Results2017"
author: "KP"
date: "01/06/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
source("SmallLakesDB.R")
ls()
```

## Methods

The mass of individual rainbow trout and eastern brook trout measured only for fork length (`r paste0("n=",nrow(no.wt))` and `r paste0("n=",nrow(no.wt.EB))`, respectively) was predicted using the log length to mass relationship from individual fish measured for both fork length and mass (`r paste0("n=",nrow(wt.EB))` and `r paste0("n=",nrow(wt.EB))`, respectively) and then back-transformed following Ogle (2016). 


Ages were predicted for individual fish without measured ages using a length-age key (n=`r nrow(RB.noages.lk.catch)`). However, fish smaller than `r lcat10.toosmall.current` mm were not sampled for age and therefore the age of these fish could not be predicted (n=`r n.toosmall.current`). 


The relationship between mass and length for the catch in 2017 is shown in Figure FLWT. Eastern brook trout gained mass more quickly than rainbow trout as their length increased (p `r fit.growth.p`)



## Tables

Table 1. Summary of catch for Boot Lake gillnet sampling in September 2017. Catch was summarized by number of fish caught (n), fork length (FL; mm), mass (M; g), and condition factor (K) mean and range. Catch-per-unit-effort (CPUE) is calculated as number of fish caught per hour of gillnet fishing.
```{r Tables, echo=F, results='asis'}
library(knitr)
kable(Table1.boot)

```

## Figures

```{r Figure.env, echo=F, results='asis', warning = FALSE, fig.height=4, fig.width=6, fig.cap= "Figure env: Vertical profile of temperature and dissolved oxygen at a deep part of Boot Lake in September, 2017"}
plot(Figure.env)

```

```{r FigureFL-wtRB-EB, echo=F, results='asis', warning = FALSE, fig.height=8, fig.width=6, fig.cap= "Figure : Length-mass relationship of rainbow (blue triangles) and brook trout (pink circles) catch from Boot Lake 2017. The top panel shows the fork length to mass relationship with a loess smoother, and the bottom panel is log10 transformed with a linear regression line and equation of relationship. The shaded area around the lines are SE."}
plot(stackplots.FLwtALL)

```


```{r FigureFL-wt-yrs, echo=F, results='asis', warning = FALSE, fig.height=8, fig.width=6, fig.cap= "Figure FL-wt: Length-mass relationship between surveys in September 2002 and September 2017 at Boot Lake. The top panel shows the fork length to mass relationship with a loess smoother, and the bottom panel is log10 transformed with a linear regression line and equation of relationship. The shaded area around the lines are SE."}
plot(stackplots.FLwtALL)

```





