---
title: "Moose Results"
author: "KP"
date: "20/05/2020"
output:
  word_document:
    reference_docx: "Template_doc.docx"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
source("SmallLakesDB.R")
ls()
```
## Methods
Ages were predicted for individual fish without measured ages using a length-age key (n=`r nrow(RB.noages.lk.catch)`). However, fish smaller than `r lcat10.toosmall.current` mm were not sampled for age and therefore the age of these fish could not be predicted (n=`r n.toosmall.current`). 


## Results
Gillnets were soaked for a total of `r round(sum(Table1.moose[,"Soak Time (hrs)"]),2)` hours and a total of `r sum(Table1.moose$n)` rainbow trout were caught. The CPUE was `r round(sum(Table1.moose$n)/sum(Table1.moose[,"Soak Time (hrs)"]),2)` fish per net-hour and was approximately equal between the floating and sinking nets (Table 1). 

The relationship between mass and length for the catch in 2017 is shown in Figure FLWT. There was no significant difference between the 2013 and 2017 logFL~logM relationship (not shown, p=`r round(car::Anova(fit2.rb)[3,4],3)`).



## Tables

Table 1. Summary of catch for Moose Lake gillnet sampling in July 2017. Catch was summarized by number of fish caught (n), fork length (FL; mm), mass (M; g), and condition factor (K) mean and range. Catch-per-unit-effort (CPUE) is calculated as number of fish caught per hour of gillnet fishing.
```{r Tables, echo=F, results='asis'}
library(knitr)
kable(Table1.moose)

```


## Figures


```{r Figure1, echo=F, results='asis', fig.height=6, fig.width=6, fig.cap= "Figure 1: The frequency of measured fork lengths of rainbow trout coloured by maturity caught in the gillnet sampling of Moose Lake in July 2001, June 2013 and July 2017. Maturity codes indicate: IM/ST = Immature or Sterile, M = Mature, MT = Maturing, SP = Spent, UNK = unknown, or NA = not checked."  }
Figure.FL.yr

```

```{r Figure2, echo=F, results='asis', warning = FALSE, fig.height=7, fig.width=6, fig.cap= "Figure 2: Length-mass relationship of catch from Moose Lake 2017. The top panel shows the fork length to mass relationship with a loess smoother, and the bottom panel is log10 transformed with a linear regression line. Circles represent mass as measured in the field, and triangles represent fish where only fork length was measured and mass predicted from the log-log linear regression. The shaded area around the lines are SE."}
plot(stackplots.FLwt)

```


```{r Figure3, echo=F, results='asis', fig.height=6, fig.width=6, fig.cap= ""  }
print(lk.overview.map)
```

```{r Figure4, echo=F, results='asis', fig.height=6, fig.width=6, fig.cap= "Figure 4: Fulton's condition factor from the three most recent Moose Lake surveys in July 2001, June 2013 and July 2017. Fish are coloured by stock category based on fork length: Sub_stock < 200 mm, Stock between 200 and 400 mm, Quality between 400 and 550 mm and Trophy > 550mm."}
Figure.K.lk

```

```{r Figure5, echo=F, results='asis', fig.height=4, fig.width=6, fig.cap = "Figure 5: Length at age with Von Bertallanfy growth curve for catch in June 2013 and July 2017. Circles are measured ages and triangles are ages predicted from an age-length key. Points were jittered horizontally at each age for improved viewing."}

fish.ages.plot

