---
title: "OneIsland_results2017"
author: "KP"
date: "21/04/2021"
output:
  word_document:
    reference_docx: "Template_doc.docx"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
source("SmallLakesDB.R")
ls()
```

## Methods

*** Doesn't apply: The mass of individual rainbow trout and eastern brook trout measured only for fork length (`r paste0("n=",nrow(no.wt))` and `r paste0("n=",nrow(no.wt.EB))`, respectively) was predicted using the log length to mass relationship from individual fish measured for both fork length and mass (`r paste0("n=",nrow(wt))` and `r paste0("n=",nrow(wt.EB))`, respectively) and then back-transformed following Ogle (2016). 


*** Does not apply: Ages were predicted for individual fish without measured ages using a length-age key (n=`r nrow(RB.noages.lk.catch)`). However, fish smaller than `r lcat10.toosmall.current` mm were not sampled for age and therefore the age of these fish could not be predicted (n=`r n.toosmall.current`). 


Ages were predicted for individual EB from `r noquote(yr.select)` without measured ages using a length-age key (n=`r nrow(EB.noages.lk.catch)`) from individuals with length and age measured (n=`r nrow(EB.ages.lk.catch)`). For comparison, ages were predicted for individual EB from `r noquote(yr.prev)` without measured ages using a length-age key (n=`r nrow(EB.noages.lk.catch.prev)`) from individuals with length and age measured (n=`r nrow(EB.ages.lk.catch.prev)`, Ogle (2016)).

## Results

The relationship between mass and length for the catch in 2017 is shown in Figure FLWT. In 2017, eastern brook trout gained mass slightly more quickly than rainbow trout as their length increased (p = `r round(fit.growth.p,3)`. From 2003 to 2017, the gain of mass per increment of fork length did not differ greatly for rainbow trout (p = `r p.flwtyrs.RB`), but eastern brook trout gained mass slightly faster (p = `r p.flwtyrs.EB`).


## Tables

Table 1. Summary of Eastern Brook Trout (EB) and Rainbow Trout (RB) catch during One Island Lake gillnet sampling in September 2017. Catch was summarized by number of fish caught (n), fork length (FL; mm), mass (M; g), and condition factor (K) mean and range. Catch-per-unit-effort (CPUE) is calculated as number of fish caught per hour of gillnet fishing.
```{r Tables, echo=F, results='asis'}
library(knitr)
kable(Table1.one.isl)

```

## Figures

```{r Figure.env, echo=F, results='asis', warning = FALSE, fig.height=4, fig.width=6, dpi=300,fig.cap= "Figure 3: The vertical lake profile of temperature (degrees C) and dissolved oxygen (mg/L) on 22 Sept. 2017. Location of where the profile was taken is shown in Figure 1."}
plot(Figure.env)

```

```{r Figure-FL freq, echo=F, results='asis', warning = FALSE, fig.height=6, fig.width=6, dpi=300,fig.cap= "Figure 4. The frequency of measured fork lengths of Eastern Brook Trout (EB, pink bars), Rainbow Trout (RB, blue bars) caught in gillnet sampling of One Island Lake in July 2003, Sept. 2012, June 2014 and Sept. 2017."}
plot(Figure.FL.yr.box)

```

```{r Figure-K freq RB, echo=F, results='asis', warning = FALSE, fig.height=6, fig.width=6, dpi=300,fig.cap= "Figure condition: Frequency of Fulton's condition factor from Rainbow Trout caught in July 2003, Sept. 2012, June 2014 and Sept. 2017. Colour of bars correspond to lengths: Sub_stock = < 200 mm, Stock = 200 to 400 mm, Quality = 400 to 550 mm and Trophy > 550 mm. Vertical dotted line indicates a condition factor of 1."}
plot(Figure.K.lk)
```

```{r Figure-K freq EB, echo=F, results='asis', warning = FALSE, fig.height=6, fig.width=6, dpi=300,fig.cap= "Figure condition: Frequency of Fulton's condition factor from Eastern Brook Trout caught in July 2003, Sept. 2012, June 2014 and Sept. 2017. Colour of bars correspond to lengths: Sub_stock = < 200 mm, Stock = 200 to 400 mm, Quality = 400 to 550 mm and Trophy > 550 mm. Vertical dotted line indicates a condition factor of 1."}
plot(Figure.K.lk.EB)
```


```{r FigureFL-wtRB-EB, echo=F, results='asis', warning = FALSE, fig.height=8, fig.width=6, dpi=300,fig.cap= "Figure : Length-mass relationship of Rainbow Trout (blue triangles) and Brook Trout (pink circles) catch from One Island Lake in 2017. The top panel shows the fork length to mass relationship with a loess smoother, and the bottom panel is log10 transformed with a linear regression line and equation of relationship. The shaded area around the lines are SE."}
plot(stackplots.FLwtALL)

```


```{r FigureFL-wt-yrs, echo=F, results='asis', warning = FALSE, fig.height=4, fig.width=6, dpi=300,fig.cap= "Figure : Log fork length versus log mass comparing Eastern Brook Trout (left panel) and Rainbow Trout (right panel) from a previous survey in 2003 with the 2017 survey. The lines are linear regression of each year’s measurements with standard error shading. All lengths between 130 and 162 mm were removed to better compare 6- and 7-panel nets."}
plot(Figure.FLwt.compare)

```


```{r Figure RB ages freq, echo=F, results='asis', warning = FALSE, fig.height=4, fig.width=6, dpi=300, fig.cap= "Figure : Frequency of ages of Brook Trout (EB) and Rainbow Trout (RB) in 2003 and 2017"}
plot(Figure.age.hist.yr)

```

```{r Figure RB ages vonB, echo=F, results='asis', warning = FALSE, fig.height=8, fig.width=6, dpi=300, fig.cap= "Figure : Fork length at ages of Rainbow Trout (RB) and Brook Trout (EB) in 2003 and 2017"}
plot(fish.ages.noVonB)

```